Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-07 ms.tex
cpation update

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
\caption{Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run. Each panel is 4 kpc x 4 kpc. The full movie of this evolution is included for further clarification of the comparison between this figure and Fig.~\ref{fig:panel2}.}
\label{fig:panel1}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
\caption{Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run. Each panel is 4 kpc x 4 kpc. The full movie of this evolution \textbf{from 0 to 118 Myr} is included for further clarification. \textbf{This movie demonstrates that the differences in outflows between the simulations depends on the ability for feedback to carve low-density, ionized channels along which SNe can launch gas beyond the disk of the galaxy. These channels are readily created by ionizing radiation in the fiducial simulation, or to some degree by SNe in the noRT simulation due to its much higher SN rate. However, SNe launched gas is trapped by neutral, cold shells in the shortrad simulation, unable to easily escape from the disk of the simulated galaxy. These same insights can also be gained by comparing this figure with Figure~\ref{panel2}.}}
\label{fig:panel1}}
\label{fig:panel1}
\end{figure*}
